---
title: "text mining"
author: "Tong Sun"
date: "12/1/2021"
output: pdf_document
always_allow_html: true
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidytext)
library(tidyr)
library(dplyr)
library(stringr)
library(ggplot2)
library(gutenbergr)
library(wordcloud)
library(reshape2)
# options(warn = -1)
```

Firstly, I would like to tidy the data.Annotate a 'linenumber' quantity to keep track of lines in the original format and a 'chapter'(with a regex) to find where all the chapters are.

```{r, echo=FALSE}
## Download the book from gutenberg
jane <- gutenberg_download(1260)
original_books <-jane %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>%
  unnest_tokens(word, text)

original_books
## Restructure into the one-token-per-row format with 'unnest_tokens()' function. Here the tokenizing is for words
tidy_books<-original_books %>%
  unnest_tokens(word, word)
```


### Task three

Truenumbers (TN) is a system for building data resources that are hosted on a server and accessed through clients that interact with with server through the Truenumbers API. The system uses natural language descriptions of data items and includes a tagging function for augmenting data items, defining subsets, and tracking process metadata. Following I would like to use TN to do analysis on Eyre book.

In this part, I used the tnum package to explore and tag text from the book Jane Eyre. I explored the frequency of words and characters throughout each section of the book, and created visualizations to show these frequencies. The process is described in more detail below.
## Download packages and the book

```{r, include=FALSE, echo=FALSE}
## Install the R tnum package 
library(devtools)
devtools::install_github("Truenumbers/tnum/tnum")

#'tnum' package
library(knitr)
library(gutenbergr)
library(tidyverse)
library(tnum)

tnum.authorize("mssp1.bu.edu")
tnum.setSpace("test2")

#jane_eyre<-gutenberg_download(gutenberg_id = 1260)  ## download Jane Eyre
jane_eyre_txt<-readLines("jane.txt")
source("Book2TN-v3-hw.R", echo = TRUE)

#tnBooksFromLines(jane_eyre_txt, "je")


## not run: tnBooksFromLines(jane_eyre$text, "jane_eyre") -- it took me a very long time

tnum.getDBPathList(taxonomy = "subject", levels = 2) # make sure the book be ingested properly
```

Assign the return from 'tnum.query' function to a variable so that we can examine the list items in the environment. And then convert the TN list to a data frame (use the 'tnum.objectstoDF()' function) so that each TN is a row in the data frame.

```{r, echo=FALSE}
q111 <- tnum.query(query = "jane_eyre# has ordinal", max=500)   ## everything
df111 <- tnum.objectsToDf(q111)

## show ordered objects in document
q112 <- tnum.query("jane_eyre# has ordinal")   ## show ordered objects in document
df112 <- tnum.objectsToDf(q112)

## focus on one paragraph -- note the word count for each sentence
q3 <- tnum.query("jane_eyre/section:0001/paragraph:0005# has count#")  # just 1 para
df3 <- tnum.objectsToDf(q3) %>% filter(date == "2021-12-03")


## and now look at the text in a sentence
q1 <- tnum.query("jane_eyre/section:0001/paragraph:0005/sentence:0002# has text")
df1 <- tnum.objectsToDf(q1) %>% filter(date == "2021-12-03")


## To extract a paragraph of text
q4 <- tnum.query("jane_eyre/section:0001/paragraph:0005/sentence# has text", max = 10)
df4 <- tnum.objectsToDf(q4) %>% filter(date == "2021-12-03")
para_text4 <- df4 %>% pull(string.value) %>% 
                      str_replace_all("\"","") %>% 
                      str_flatten(collapse = " ")

## steps to understand
# a <- para_text4[1]
# a
# 
# b <- str_replace_all(a,"\"","")   
# b
# 
# c <- para_text4
# c
# 
# c <- str_replace_all(a,"\"","")  
# 
```

## Use tnum in text analysis

In this part, I want to use TNs for text analysis. As I did before, loading the libraries I need, authorizing the server if needed and setting the number space to "test2"

```{r, echo=FALSE}
##  The ordinal numbers for the entire book 
##  show the sequence of objects in order of their appearance.
w10 <- tnum.query("jane_eyre# has ordinal", max=1800)
wdf10 <- tnum.objectsToDf(w10)

## Examing the first 50 TNs  makes it easy to see the Table of Contents
## and to see that object 11 is the heading at the start of Chapter 1


## This shows the Table of Contents
w11 <- tnum.query("jane_eyre# has text", start = 3 ,max=18)
wdf11 <- tnum.objectsToDf((w11))

table_of_contents <- wdf11 %>% select(string.value) 


## Look at just the headings shows the structure of the book
w13 <- tnum.query("jane_eyre/heading# has text", max=40)
wdf13 <- tnum.objectsToDf(w13)


## It may look like the table of contents is repeated twice,
## but examing the ordinals produces chapter list that includes the 
## ordinal location for the heading of each chapter
w14 <- tnum.query("jane_eyre/heading# has ordinal", max=40)
wdf14 <- tnum.objectsToDf(w14)

chapter_locations <- left_join(select(wdf13, subject, string.value), 
                               select(wdf14, subject, numeric.value)) 
## add column for chapter number
library(magrittr)
chapter_locations %<>% mutate(chapter=1:36) # because there are 36 chapters in total

w15 <- tnum.query("jane_eyre/section:0011# has ordinal")
wdf15 <- tnum.objectsToDf(w15)



## chapter 1 para 1, word counts for the 3 sentences in para 1
q20 <- tnum.query("jane_eyre# has *", max=3)
df20 <- tnum.objectsToDf(q20)

#  chapter locations  ordinal numbers
ord_ch1 <- unlist(tnum.query("jane_eyre/heading:0011# has ordinal"))
ord_ch2 <- unlist(tnum.query("jane_eyre/heading:0012# has ordinal"))


ch1_txt <- tnum.query("jane_eyre/section:0011/paragraph:0002/# has text", max=30)

ch1_txt_df <- tnum.objectsToDf(ch1_txt)
ch1_txt_df$string.value

ch2_txt <- tnum.query("jane_eyre/section:0011/paragraph:0002/sentence:# has *", max=30)
ch2_txt_df <- tnum.objectsToDf(ch2_txt)

ch2_txt_df$string.value

length(ch2_txt_df$string.value)


q21 <- tnum.query("jane_eyre/section:0011/paragraph:0001/# has *", max = 30)
df21 <- tnum.objectsToDf(q21)
```

## Sentimentr

Sentimentr is designed to quickly calculate text polarity sentiment in the English language at the sentence level and optionally aggregate by rows or grouping variable(s).

```{r, echo=FALSE,message=FALSE,warning=FALSE}
library(sentimentr)
jane_1 <- get_sentences(para_text4)

## Get sentiment scores by sentence
a<-sentiment(jane_1) # The sentiment scores here are all zero.

## Get sentiment scores aggregated by paragraph
b<-sentiment_by(jane_1)

c<-emotion(jane_1)

## Rename the data to 'jan_senti' after getting sentences from original book
jan<-tidy_books
jan %>%
  get_sentences() %>%
  sentiment() -> jan_senti
## See the density plot of sentiment
jan_senti %>%
  ggplot() + geom_density(aes(sentiment))
## Mutate 'polarity_level' to see differences between positive and negative
jan_senti %>%
  mutate(polarity_level = ifelse(sentiment > 0, "Positive", "Negative")) %>%
  count(linenumber, polarity_level) %>%
  ggplot() + geom_col(aes(y = linenumber, x = n, fill = polarity_level)) +
  theme_minimal()
```

From the density plot, we can see most of the sentiments are zero. For the plot with 'polarity_level', each linenumber has different number of positive and negative sentiments.

## Extra attempts: tag

From the content, I would like to analysis the relationship between Jane and her uncle, Reed. Firstly I create a tag to 'Jane|Reed' in order to find where they comes out together in this book.

```{r, echo=FALSE}
# Create tag
qr2<-tnum.query("jane_eyre/# has*=REGEXP(\" Jane|Reed\")",max = 50) # there are 156 results in this book.
qr_df_2<-tnum.objectsToDf(qr2)
tnum.tagByQuery("jane_eyre/# has*=REGEXP(\" Jane|Reed\")",adds = ("reference:jr")) # create the tag and give it a reference at the same time

# Make plots(before making plots, I create a function to turn all the chapters into a vector)
getdf<-function(df){
  n<-nrow(df)
  vector<- rep(0,n)
  subject<- df$subject
  for (i in 1:n) {
   vector[i]<-
      as.numeric(substring(str_split(subject[i], "/")[[1]][2], 9)) # section comes out at the second location in the split subject
  }
  return(vector)
}
# Jane and Reed
ggplot() + geom_bar(mapping = aes(getdf(qr_df_2)), stat = "count")+
  labs(x="Section", title = "Frequency of 'Jane and Reed'")
```

From the plot above, it shows that 'Jane and Reed' comes out together in several sections. The most important part is in the earlier part of the book, which makes sense. This fits the story that the book tells -- her uncle, Reed, raises Jane when she was a child.

## Show virsually

```{r, echo=FALSE}
# Create a function for paragraph number
para_num_df<-function(df){
  n<-nrow(df)
  vector<-rep(0,n)
  subject<-df$subject
  for(i in 1:n){
    vector[i]<-as.numeric(substring(str_split(subject[i],"/")[[1]][3],11))
  }
  return(vector)
}

num1<-tnum.query("jane_eyre# has count:word", max = 1500)
num1_df<-tnum.objectsToDf(num1)

word_data<-data.frame(ch = getdf(num1_df),para =para_num_df(num1_df), num = num1_df$numeric.value)

word_data<-word_data %>%
  group_by(ch) %>%
  summarise(count = sum(num))

ggplot(data = word_data, aes(x = as.factor(ch), y = count, group =1)) +
  geom_line(color = "orange") +
  geom_point() +
  labs(x = "Chapter Number", y = "Number of Words")+
  ggtitle("Word Count in Each Chapter")+
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text =  element_text(size = 7))
## Create functions for query
# For section number
ch_num<-function(query){
  n<-length(query)
  vector<-rep(0,n)
  for(i in 1:n){
    vector[i]<-as.numeric(substring(str_split(tnum.getAttrFromList(query[i],"subject"), "/")[[1]][2],9))
  }
  return(vector)
}
# For paragraph number
para_num<-function(query){
  n<-length(query)
  vector<-rep(0,n)
  for(i in 1:n){
    vector[i]<-as.numeric(substring(str_split(tnum.getAttrFromList(query[i],"subject"), "/")[[1]][3],11))
  }
  return(vector)
}

# Histogram of Occurances of the Word Jane|Reed
jr_data<-data.frame(ch = ch_num(qr2), para = para_num(qr2))
ggplot(jr_data, aes(ch)) +
  geom_histogram(aes(fill = as.factor(para)), binwidth = 1) +
  labs(title = "Distribution of The Word Jane|Reed") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(fill = "Paragraph Number") +
  xlab("Section Number")
# Show relationship
jrgraph<-tnum.graphTnumList(qr_df_2$subject)
# Not work well: tnum.plotGraph(jrgraph)
```

This part I would like to show the relationship between Jane and Reed, but I cannot use the function such as 'tnum.plotGraph()' in the file you showed us in class. There is an error saying these functions do not exist. What I can do is drawing a plot showing the distribution of the Word 'Jane|Reed' occurances. I will work on the part that does not go well in the future.
